Enhancement of SDR in Thessaloniki

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 17:11

@@

\begin{verbatim}
2024-02-29 11:01:18.2 athan@tyler GHI_enh_04_investigate.R 1.255829 mins
\end{verbatim}

>>>>

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-8} \end{center}

@@

\begin{verbatim}
2024-02-29 14:29:51.0 athan@tyler GHI_enh_04_investigate.R 1.085176 mins
\end{verbatim}
